Parallelizing AdaBoost and Decision Trees

### 2015-08-21 paper.tex
paper changes

The goal of this project is to implement a parallelized version of a commonly
used weak learner, decision trees, to improve the running time of AdaBoost. We
give a short overview of AdaBoost and decision trees in the next section,
describe the implementation of the decision trees, the data sets used and the
results t

>>>>

The goal of this project is to implement a parallelized version of a commonly
used weak learner, decision trees, to improve the running time of AdaBoost. We
give a short overview of AdaBoost and decision trees in the next section,
describe the implementation of the decision trees, the data sets used and the
results comparing the serial and parallelized execution of the boosting algorithm.
